### 2022-02-15 introduction/introduction.tex
more

\section{Contribution}

@@

>>>>

\section{Contributions}

@@

  \item Taking all the experience we gathered while working on Zipperposition,
  we further extended Ehoh to full higher-order logic. Here again modified term
  structure, implemented new unification and matching algorithms, extended indexing data
  structures, and tweaked heuristics. Even though this extension has larger scope than 
  the original extension from E to Ehoh, strong basis that we have earlier built
  made it manageable.
